\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-03-25 doc/sw-cfhtls.tex
Implemented \StageOne and \StageTwo macros, closes #109

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps II: CFHTLS 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%
%\subsection{Paper I: Overview}
%In Paper I, we give details of the classification interface used by the
%volunteers. The regular images called test subjects are served randomly from the
%database. Some of the test subjects are labelled as training subjects because
%either these have simulated lensed images superposed around real galaxies or
%there are some false positives in the subjects.  The sample of training subjects
%is much smaller compared to the sample of test subjects. The training subjects
%are shown with decreasing frequency to the volunteers depending on how new the
%volunteers are to the project based on their classification history. However,
%the frequency of training subjects becomes a constant after XXX classifications
%from a volunteer.
%
%Clicking (or failing to click) on the training subjects results in a
%pop-up feedback message that congratulates the volunteers or points them
%to read the Spotter's guide pages. The website has several examples of
%real lenses and false positives with explanation on the Spotter's guide
%page. A quick reference to the Spotter's guide is available in the
%classification interface as well. Additional features to change zoom,
%contrast and brightness are made available to make a better judgement of
%the difficult lens candidates.
%
%The classification of subjects happens in two serial stages. Stage I is
%for quick rejection of all uninteresting subjects. Subjects that passed
%Stage I are then reinspected at Stage II, for a careful selection of
%most promising lens candidates. In general, subjects are assigned a
%small prior probability for it to contain a lens. As each subject is
%seen by multiple volunteers, the posterior probability P is updated by
%using the weights of the volunteers. The weights are determined based on
%how well the volunteers perform on the training sample. Once a subject
%crosses a threshold (acceptance or rejection), it is retired from the
%database to ensure that rest of the subjects receive sufficient multiple
%classifications. This is true for stage I with ~10$^5$ subjects but is
%not required for stage II with only a few thousand subjects.
%
%{\bf AM: add one more paragraph that gives some key conclusions and numbers
%from Paper I}
%\question{AM}{PJM,AV, should we have this overview section on paper I?}
%

@@

We selected a sample of 450 duds for the Stage I classification in \sw
and a sample of 500 false positives for the Stage II inspection. The
sample of false positives was selected from the candidates which passed
the Stage I of \sw. We note that this is the first time, we have a
systematically compiled sample of visually inspected false positives by
the \sw volunteers and categorized by the science team. The data products are
available at http://spacewarps.org/\#/projects/CFHTLS/. Such a sample is
tremendously helpful for training and understanding performances of
various lens finding algorithms \citep{Chan2014}.

@@

The \sw works as a single unified neural network which uses the method of visual
inspection to find gravitational lenses. The volunteers are shown images at two
stages. At stage I, volunteers are requested to undertake a rapid inspection to
select lens candiates ranging from possible lenses to almost certain lenses. At
stage II, volunteers carefully inspect the candidates from stage I and select only
promising lens candidates. A daily snapshot of classifications performed by
volunteers are provided to the science team every night. This daily batch is
analyzed by the Space Warps Analysis Pipeline (SWAP). The philosophy and the
details of SWAP are described in detail in Paper I, here we briefly summarize
how it works.

@@

SWAP was run nightly during Stage I in order to retire subjects and inject new
ones in to the classification stream. The subjects that passed the acceptance
threshold at the end of Stage I are served again at Stage II for careful
reinspection. Each subject, after Stage II, has an associated posterior
probability P. In the ideal case, all images containing lenses will have high P
values and those without lenses will have low P values. In practice, we expect a
small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
values and thus, decreasing the completeness (or purity) of the final lens
sample.  As this is the first candidate search with \sw, we want to find a
threshold P value which will result in acceptable levels of completeness and
purity of the final sample of lens candidates.

@@

In Table~\ref{tab:stats}, we give overall statistics of the systems detected at
stage I and stage II. We give the total number of detections of the known lens
candidates, known lenses and the new lens candidates at each stage.  We also
show their fractions with respect to the total number of lens candidates found
at these stages. We note that most (XXX check) of the confirmed lenses found at
stage I are also recovered at stage II whereas a small fraction of the known
lens candidates are rejected at stage II. Also, the sample of new lens
candidates increases the sample of \cfhtls lens candidates by over 50\%.

In \Fref{fig:stackP}, we plot the distribution of false positives and the high
probability lens candidates, categorized by the lens experts, as a function of
the P value assigned by SWAP at the end of Stage II. On average, the fraction of
lens candidates is indeed an increasing function of P. This shows that the \sw
generated P values for the subject are roughly correlated with the expert grades
albeit with quite some scatter.  We note that from P$\sim$0.75 onwards to lower
P values, the fraction of false positives starts to exceed the fraction of real
lens candidates. This could be a good threshold to choose to maximize the purity
of the final sample. However, the choice of P$=$0.3 as the threshold gives a
more acceptable completeness of XXX for our sample which combined with expert
grading allows us to achieve further purity of our sample.
{\bf AM: give some numbers for the completeness/purity ?}

\begin{table}
\begin{center}
\caption{ \label{tab:stats} 
Statistics of detections in \sw }
\begin{tabular}{l l l l l l l}
\hline
   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{4}{c}{Stage II} \\ 
      & KC  &  KL  & KC & KL & NC & AC\\
\hline
\hline
Number  & 128 & 34 & 107  & 34  & 61 & 168\\
\%  & 29 & 58 & 25 & 58  & 12 & 34\\
P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 & 0.3\\

@@

We give details of the final sample of 61 new lens candidates found by \sw in
Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name of the
lens system. We give their positions (Ra, Dec), photometric redshift
($z_{phot}$), $i$ band magnitude of the lensing galaxy, averaged grade G from
the lens experts, zoo ID (identifier used in
TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for \sw), P
value at stage II and a visual categorization of type of lensed images and the
lensing galaxy in the Comments column in Table~\ref{tab:swcands}. Whenever
available the lens properties are taken from the \cfhtls photometric catalog
\citep{Coupon2009} otherwise the reported lens galaxy positions are measured
manually. The visual categorization of the lens type is only suggestive and the
explanation of the notations in the Comments column is given at the bottom of
the table.

@@

We determine what fraction of the known sample of lenses are recovered
by \sw. In Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the
known candidates and $\sim$~60\% of the known lenses are found at stages
I and II in \sw. The left and the middle panels of \Fref{fig:compre}
show the fraction of detections as a function of arc magnitude and the
Einstein radius of the lens systems for the known confirmed lenses and
lens candidates. As expected, we find that systems with brighter images
and/or with larger Einstein radii are detected more often in \sw.

@@

%Lastly, we attempt to characterize the completeness of the \sw lens
%sample based on the simulated lens sample. The right most panel of
%\Fref{fig:compre} shows the completeness of the simulated sample
%at stage I of \sw as a function of the arc magnitude and Einstein
%radius. We find that the lens sample is more than XXX\% complete between image
%separations 2"-10".

@@

\subsection{False negatives: known lenses missed by \sw}
\label{sec:fn}
Like any lens finding method, the \sw system can fail to detect certain
kinds of lenses.  We find that about 40\% of the known sample of lenses
are missed both at stage I and II (see \Tref{tab:stats}). In fact, most
of the known lenses from stage I are discovered at stage II suggesting
that most lenses are lost right at stage I. Below, we focus on the known
lens sample at stage I to understand why some of them are being missed
and possibly find a way to improve the detection rate which can be
adopted in the future \sw lens searches.

@@

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at stage I (reached high P even with fewer classifications) and missed at stage II (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at stage I XXX}
%One of those 6 lenses was detected at stage I but failed to get high enough P value at stage II even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at stage I. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy

@@

We check how the posterior probability P (see Paper I for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
examples of detected lenses (top left panels) and missed lenses (bottom
left panels) by \sw at stage I. The number of classifications (Nclass)
for a subject increase from top to bottom.  Also, every subject is
assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
starts at the middle of the trajectory plot. The P value of a subject is
updated with every classification from the volunteer.  If a volunteer
identifies a lens candidate, the trajectory moves to the right otherwise
moves to the left. A subject is accepted if it crosses the blue-dashed
line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
rejected, if it crosses the red-dashed line marking the P$_{\rm rej
thresh}=10^{-7}$ on the left.

@@

We rerun SWAP for stage I where we use classifications from volunteers
who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
the total Nclass per subject by a large fraction. As a result, we also
need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
find that about a third of the missed lenses are detected while all the
previously detected lenses remain detected too. The others simply do not
have enough classifications from volunteers producing large positive
kicks. Thus, it may be possible to detect more promising candidates if
we preferentially show the rejected systems to a few more skilled
volunteers. We understand that changing the rejection and acceptance
thresholds will likely increase the rate of FPs along with
improved completeness but most probably the increase in FPs will not be
too significant and that it will still be worth using the new strategy.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_traj.pdf}
\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_hist.pdf}
\caption{ \label{fig:detmis}
Examples of trajectories of some known lenses (top-left: detected and
bottom-left: missed) at stage I and histogram of the known lenses for
different types of volunteers (right). Among the sample of missed
lenses, most classifications are from the less skilled volunteers
identifying these images incorrectly (i.e. $-\Delta$~logP) which
overshadows the small number of correct identifications (i.e.
$\Delta$~logP) coming from both the less and the more skilled volunteers
combined. For the detected lens sample, most classifications are correct
identifications coming from both less and more skilled volunteers.
}
\end{center}
\end{figure*}

@@

The blind lens search in the \cfhtls is done in two stages: stage I and
stage II. In stage I, volunteers inspected $\sim$ 430 000 subjects and
selected a smaller sample of $\sim$ 3000 subjects with interesting lens
candidates. In stage II, after a careful reinspection of the candidates
from stage I, a smaller pool of more pure sample of $\sim$~500
candidates is obtained. In the next step, the images are graded by three
lens experts (AM, AV and PJM) producing candidates that range from
mildly interesting to certainly a lens system.

@@

\item Based on the known sample of lenses and lens candidates, we find
that we lose a very small fraction of them as we go from Stage I to
Stage II. In other words, it is more important to improve the lens
detection efficiency right at Stage I to increase the overall
completeness of the final lens sample

\item From the sample of known lenses, \sw missed about 40\% at Stage I.
Among the missed sample of about 20 lenses, roughly half of them are
visually difficult to identify because most of them are faint with small
image separations which are identified through the \rf

\item If we use the classifications from more skilled volunteers alone
at Stage I, then we recover over 30\% of the lenses from the missed
sample. Thus, it is possible to improve the completeness of lenses by
changing the strategy of when and who is shown an image.

@@

%{\bf todo: run swap and extract the status of all the known lens candidates
%-- because the undecided are not known otherwise. fig will have to be
%updated for the blind lens search section; also check what happened to
%those AF lenses which were labelled sims - look at the D11 counterparts
%and their status in stage 1 swap}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps Paper II: CFHTLS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%
%\subsection{Paper I: Overview}
%In Paper I, we give details of the classification interface used by the
%volunteers. The regular images called test subjects are served randomly from the
%database. Some of the test subjects are labelled as training subjects because
%either these have simulated lensed images superposed around real galaxies or
%there are some false positives in the subjects.  The sample of training subjects
%is much smaller compared to the sample of test subjects. The training subjects
%are shown with decreasing frequency to the volunteers depending on how new the
%volunteers are to the project based on their classification history. However,
%the frequency of training subjects becomes a constant after XXX classifications
%from a volunteer.
%
%Clicking (or failing to click) on the training subjects results in a
%pop-up feedback message that congratulates the volunteers or points them
%to read the Spotter's guide pages. The website has several examples of
%real lenses and false positives with explanation on the Spotter's guide
%page. A quick reference to the Spotter's guide is available in the
%classification interface as well. Additional features to change zoom,
%contrast and brightness are made available to make a better judgement of
%the difficult lens candidates.
%
%The classification of subjects happens in two serial stages. \StageOne is
%for quick rejection of all uninteresting subjects. Subjects that passed
%\StageOne are then reinspected at \StageTwo, for a careful selection of
%most promising lens candidates. In general, subjects are assigned a
%small prior probability for it to contain a lens. As each subject is
%seen by multiple volunteers, the posterior probability P is updated by
%using the weights of the volunteers. The weights are determined based on
%how well the volunteers perform on the training sample. Once a subject
%crosses a threshold (acceptance or rejection), it is retired from the
%database to ensure that rest of the subjects receive sufficient multiple
%classifications. This is true for \StageOne with ~10$^5$ subjects but is
%not required for \StageTwo with only a few thousand subjects.
%
%{\bf AM: add one more paragraph that gives some key conclusions and numbers
%from Paper I}
%\question{AM}{PJM,AV, should we have this overview section on paper I?}
%

@@

We selected a sample of 450 duds for the \StageOne classification in \sw
and a sample of 500 false positives for the \StageTwo inspection. The
sample of false positives was selected from the candidates which passed
the \StageOne of \sw. We note that this is the first time, we have a
systematically compiled sample of visually inspected false positives by
the \sw volunteers and categorized by the science team. The data products are
available at http://spacewarps.org/\#/projects/CFHTLS/. Such a sample is
tremendously helpful for training and understanding performances of
various lens finding algorithms \citep{Chan2014}.

@@

The \sw works as a single unified neural network which uses the method of visual
inspection to find gravitational lenses. The volunteers are shown images at two
stages. At \StageOne, volunteers are requested to undertake a rapid inspection to
select lens candiates ranging from possible lenses to almost certain lenses. At
\StageTwo, volunteers carefully inspect the candidates from \StageOne and select only
promising lens candidates. A daily snapshot of classifications performed by
volunteers are provided to the science team every night. This daily batch is
analyzed by the Space Warps Analysis Pipeline (SWAP). The philosophy and the
details of SWAP are described in detail in Paper I, here we briefly summarize
how it works.

@@

SWAP was run nightly during \StageOne in order to retire subjects and inject new
ones in to the classification stream. The subjects that passed the acceptance
threshold at the end of \StageOne are served again at \StageTwo for careful
reinspection. Each subject, after \StageTwo, has an associated posterior
probability P. In the ideal case, all images containing lenses will have high P
values and those without lenses will have low P values. In practice, we expect a
small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
values and thus, decreasing the completeness (or purity) of the final lens
sample.  As this is the first candidate search with \sw, we want to find a
threshold P value which will result in acceptable levels of completeness and
purity of the final sample of lens candidates.

@@

In Table~\ref{tab:stats}, we give overall statistics of the systems detected at
\StageOne and \StageTwo. We give the total number of detections of the known lens
candidates, known lenses and the new lens candidates at each stage.  We also
show their fractions with respect to the total number of lens candidates found
at these stages. We note that most (XXX check) of the confirmed lenses found at
\StageOne are also recovered at \StageTwo whereas a small fraction of the known
lens candidates are rejected at \StageTwo. Also, the sample of new lens
candidates increases the sample of \cfhtls lens candidates by over 50\%.

In \Fref{fig:stackP}, we plot the distribution of false positives and the high
probability lens candidates, categorized by the lens experts, as a function of
the P value assigned by SWAP at the end of \StageTwo. On average, the fraction of
lens candidates is indeed an increasing function of P. This shows that the \sw
generated P values for the subject are roughly correlated with the expert grades
albeit with quite some scatter.  We note that from P$\sim$0.75 onwards to lower
P values, the fraction of false positives starts to exceed the fraction of real
lens candidates. This could be a good threshold to choose to maximize the purity
of the final sample. However, the choice of P$=$0.3 as the threshold gives a
more acceptable completeness of XXX for our sample which combined with expert
grading allows us to achieve further purity of our sample.
{\bf AM: give some numbers for the completeness/purity ?}

\begin{table}
\begin{center}
\caption{ \label{tab:stats}
Statistics of detections in \sw }
\begin{tabular}{l l l l l l l}
\hline
   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{4}{c}{\StageTwo} \\
      & KC  &  KL  & KC & KL & NC & AC\\
\hline
\hline
Number  & 128 & 34 & 107  & 34  & 61 & 168\\
\%  & 29 & 58 & 25 & 58  & 12 & 34\\
P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 & 0.3\\

@@

We give details of the final sample of 61 new lens candidates found by \sw in
Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name of the
lens system. We give their positions (Ra, Dec), photometric redshift
($z_{phot}$), $i$ band magnitude of the lensing galaxy, averaged grade G from
the lens experts, zoo ID (identifier used in
TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for \sw), P
value at \StageTwo and a visual categorization of type of lensed images and the
lensing galaxy in the Comments column in Table~\ref{tab:swcands}. Whenever
available the lens properties are taken from the \cfhtls photometric catalog
\citep{Coupon2009} otherwise the reported lens galaxy positions are measured
manually. The visual categorization of the lens type is only suggestive and the
explanation of the notations in the Comments column is given at the bottom of
the table.

@@

We determine what fraction of the known sample of lenses are recovered
by \sw. In Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the
known candidates and $\sim$~60\% of the known lenses are found at \StageOne and \StageTwo in \sw. The left and the middle panels of \Fref{fig:compre}
show the fraction of detections as a function of arc magnitude and the
Einstein radius of the lens systems for the known confirmed lenses and
lens candidates. As expected, we find that systems with brighter images
and/or with larger Einstein radii are detected more often in \sw.

@@

%Lastly, we attempt to characterize the completeness of the \sw lens
%sample based on the simulated lens sample. The right most panel of
%\Fref{fig:compre} shows the completeness of the simulated sample
%at \StageOne of \sw as a function of the arc magnitude and Einstein
%radius. We find that the lens sample is more than XXX\% complete between image
%separations 2"-10".

@@

\subsection{False negatives: known lenses missed by \sw}
\label{sec:fn}
Like any lens finding method, the \sw system can fail to detect certain
kinds of lenses.  We find that about 40\% of the known sample of lenses
are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
of the known lenses from \StageOne are discovered at \StageTwo suggesting
that most lenses are lost right at \StageOne. Below, we focus on the known
lens sample at \StageOne to understand why some of them are being missed
and possibly find a way to improve the detection rate which can be
adopted in the future \sw lens searches.

@@

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at \StageOne XXX}
%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at \StageOne. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy

@@

We check how the posterior probability P (see Paper I for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
examples of detected lenses (top left panels) and missed lenses (bottom
left panels) by \sw at \StageOne. The number of classifications (Nclass)
for a subject increase from top to bottom.  Also, every subject is
assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
starts at the middle of the trajectory plot. The P value of a subject is
updated with every classification from the volunteer.  If a volunteer
identifies a lens candidate, the trajectory moves to the right otherwise
moves to the left. A subject is accepted if it crosses the blue-dashed
line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
rejected, if it crosses the red-dashed line marking the P$_{\rm rej
thresh}=10^{-7}$ on the left.

@@

We rerun SWAP for \StageOne where we use classifications from volunteers
who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
the total Nclass per subject by a large fraction. As a result, we also
need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
find that about a third of the missed lenses are detected while all the
previously detected lenses remain detected too. The others simply do not
have enough classifications from volunteers producing large positive
kicks. Thus, it may be possible to detect more promising candidates if
we preferentially show the rejected systems to a few more skilled
volunteers. We understand that changing the rejection and acceptance
thresholds will likely increase the rate of FPs along with
improved completeness but most probably the increase in FPs will not be
too significant and that it will still be worth using the new strategy.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_traj.pdf}
\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_hist.pdf}
\caption{ \label{fig:detmis}
Examples of trajectories of some known lenses (top-left: detected and
bottom-left: missed) at \StageOne and histogram of the known lenses for
different types of volunteers (right). Among the sample of missed
lenses, most classifications are from the less skilled volunteers
identifying these images incorrectly (i.e. $-\Delta$~logP) which
overshadows the small number of correct identifications (i.e.
$\Delta$~logP) coming from both the less and the more skilled volunteers
combined. For the detected lens sample, most classifications are correct
identifications coming from both less and more skilled volunteers.
}
\end{center}
\end{figure*}

@@

The blind lens search in the \cfhtls is done in two stages: \StageOne and
\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 subjects and
selected a smaller sample of $\sim$ 3000 subjects with interesting lens
candidates. In \StageTwo, after a careful reinspection of the candidates
from \StageOne, a smaller pool of more pure sample of $\sim$~500
candidates is obtained. In the next step, the images are graded by three
lens experts (AM, AV and PJM) producing candidates that range from
mildly interesting to certainly a lens system.

@@

\item Based on the known sample of lenses and lens candidates, we find
that we lose a very small fraction of them as we go from \StageOne to
\StageTwo. In other words, it is more important to improve the lens
detection efficiency right at \StageOne to increase the overall
completeness of the final lens sample

\item From the sample of known lenses, \sw missed about 40\% at \StageOne.
Among the missed sample of about 20 lenses, roughly half of them are
visually difficult to identify because most of them are faint with small
image separations which are identified through the \rf

\item If we use the classifications from more skilled volunteers alone
at \StageOne, then we recover over 30\% of the lenses from the missed
sample. Thus, it is possible to improve the completeness of lenses by
changing the strategy of when and who is shown an image.

@@

%{\bf todo: run swap and extract the status of all the known lens candidates
%-- because the undecided are not known otherwise. fig will have to be
%updated for the blind lens search section; also check what happened to
%those AF lenses which were labelled sims - look at the D11 counterparts
%and their status in \StageOne swap}
